Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-02-07 text/src/article.tex

% }}}
% {{{ Background
\section*{Background}
 Text for this section.\cite{koon,oreg,khar,zvai,xjon,schn,pond,smith,marg,hunn,advi,koha,mouse}
% }}}
% {{{ Implementation
%%%%%%%%%%%%%%%%%%%%%%
\section*{Implementation}
  Text for this section \ldots
% }}}
\section*{Results and Discussion} %{{{1

>>>>

% }}}
% {{{ Background
\section*{Background} %{{{1

Large-scale parallel genome sequencing can produces hundreds of thousands to
millions of nucleotide reads. These reads describe the nucleotide sequence in
a region of the genome. The current status of parallel nucleotide sequencing
limits the largest read length to $>$1000 nucleotides and to obtain
a contiguous complete genome sequence these sequence reads must be joined
together. \pb

The process of joining these reads together is described as the `assembly'
stage in a genome sequencing project. Assembly software joins these numerous
sequence reads together, usually from the overlap between reads, into
contiguous regions (`contigs') composing many of the individual reads. The goal
of the assembly stage is produce a contiuous genome sequence describing the
complete genome from start to finish. \pb

These reads may however not represent a complete genome sequence where all
contigs do not result in a single complete sequence. The software outlined here
``Scaffolder'' allows these contigs to be further joined together into
a continuous single sequence. This selection, order and direction of contigs
into a final draft genome is often described as the `scaffold'. \pb

\section*{Implementation} %{{{1

  Text for this section \ldots
% }}}
\section*{Results and Discussion} %{{{1
